Fixed-Shape Ellipse by Three Points

### 2019-10-23 ONPCE/slides.tex
wip

\begin{frame}{Fixed-shape ellipse by three points}
	There is no clear pattern in $\xi$.
	\begin{itemize}
		\item It can be written as $\{\cos^j{x}\sin^k{x} : j, k \in \mathbb{N}\}$.
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
	\end{itemize}
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.5]{035}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

@@

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{012}
		\caption{Yet another example of $\xi$.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
	\end{itemize}
\end{frame}

@@

		\item Very used in practice: present in external libraries like NumPy for Python.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. This is it for $n=5$:

>>>>

\begin{frame}{Fixed-shape ellipse by three points}
	There is no clear pattern in $\xi$.
	\begin{itemize}
		\item It can be written as 
		$$\xi(\theta)=\sum_{0 \le j, k \le Deg(\xi)} \alpha_{j,k}\cos^{j}{\theta}\sin^{k}{\theta}.$$
		\item Degree $6$, at most $12$ roots in $[0, 2\pi)$ \cite[p.~150]{powell}
	\end{itemize}
\begin{figure}
	\centering

	%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
	\includegraphics[scale=.4]{012}
	\caption{Another example of $\xi$.}
	%	\label{fig:circumscribed-circle}
\end{figure}
\end{frame}

@@

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.5]{g4sol}
		\caption{An example of $\xi$ with $4$ roots.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

@@

	\begin{itemize}
		\item This can be done in $\bigO(n^3)$ \cite{boyd:2013}.
		\item A simple change of coordinates lets the interpolation to be done on any closed interval!
	\end{itemize}
\end{frame}

@@

		\item Very used in practice: 
		\begin{itemize}
			\item Present in external libraries like NumPy for Python.
			\item Matlab tool Chebfun: allows functions to be treated as vectors.
		\end{itemize}
	\end{itemize}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $8$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn8}
		\caption{An example of degree $8$ approximation.}
		%	\label{fig:circumscribed-circle}
	\end{figure}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $10$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn10}
		\caption{An example of degree $10$ approximation.}

	\end{figure}
\end{frame}

\begin{frame}{Example}
	$\xi$ and its approximation of degree $12$.
	\begin{figure}
		\centering

		%\caption{Transforming an ellipse into a circle. T1, T2, and T3 represent the steps of the transformation.}
		\includegraphics[scale=.6]{inexn12}
		\caption{An example of degree $12$ approximation.}

	\end{figure}
\end{frame}

@@

\begin{frame}{Chebyshev Interpolation}{Roots}
	The roots of a Chebyshev polynomial can be found though determining the eigenvalues of a Chebyshev companion matrix \cite{boyd:2013}. For $n=5$ we have:
